---
title: "R Markdown Documents - Part 1"
author: "Briantama Asmara"
date: "9/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Section 1

* A variable a that contains the text of your first name.
* A variable b1 that contains the number 45.6
* A variable b2 that contains the text “45.6”
* A variable c1 that contains the sequence of integers from 0 to 3

```{r}
a = "Briantama"
b1 = 45.6
b2 = "45.6"
c1 = c(0,1,2,3)
```

# Q1
```{r}
class(a)
```

# Q2
```{r}
class(b1)
```

# Q3
```{r}
class(b2)
```

# Q4
```{r, error=TRUE}
sum(b1,b2)
```
Answer: It causes an error because b1 and b2 have different data types. B1 is a numeric data, while B2 is a character data.

# Q5
```{r}
class(b1) == class(c1)
```

No, b1 is a numeric data, while b2 is a character

# Q6
```{r, error=TRUE}
class(c1)
b1+c1
```
Both of them are numerical data. It sums up all the integer numbers in c1 (0,1,2,3) to b1 (45.6). In other words, total of c1 (6) adds up to b1 (45.6), equals 51.6. It is going to be a bit different in other programming language such as Python, b1 is considered to be a float data type, while c1 is an integer. It could stir a bit of a problem when adds those two numbers, but R seems kind of make it easier to just merge them to numeric data types.


## Section 2

# Q7
```{r}
v1 = c(-2,-1,0,1,2)
v1
```

# Q8
```{r}
v2 = v1 * 3
v2
```

# Q9
```{r}
sum(v2)
```

## Section 3

```{r}
vec4 = 1:12
```



# Q10
```{r}
mat1 = matrix(vec4, byrow= TRUE, nrow = 3)
mat1
```

# Q11
```{r}
mat2 = matrix(vec4, byrow= FALSE, nrow = 3)
mat2
```

# Q12
```{r}
my_list_1 = list(two = 5.2, 
                 one = "five point two", 
                 three = 1:5)
my_list_1
```

# Q13
```{r}
my_list_1[3]
```

# Q14
```{r}
my_list_1[2]
my_list_1$one
```

# Q15
```{r}
my_vec = rep(1:3, 5)
my_vec

```
```{r}
my_bool_vec <- my_vec == 3
my_bool_vec
```

```{r}
df = data.frame(my_vec, my_bool_vec)
df
```


# Q16

```{r}
my_vec[my_bool_vec]
```
