---
title: "Part 1: R Reference Guide"
author: "Briantama Asmara"
date: "12/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Part 1: R Reference Guide {.tabset .tabset-pills}


## Loading Data and Packages
* Load here() packages and ginkgo data

```{r}
## Loading the here package to load the working directory, you need to install it first if here() didn't load
require(here)
here()

## Load the data
ginkgo = data.frame(read.csv(here("data", "ginkgo_data_2021.csv")))
head(ginkgo)
```
* Load palmer penguins

```{r}
## Load external dataset of penguins
library(palmerpenguins)
head(penguins)
```


## Data Structures
* c()

```{r}

## Assigning the values of several data
six_delomys  = c('A', 'B', 'C', 'D', 'E', 'G', 'H', 'J')
height_delomys = c(20,56,24,65,13,54,53,32)
length_delomys = c(43,125,35,13,612,63,62,53)
```

* length

```{r}
# Know the length
length = length(six_delomys)
print(paste("The length of six_delomys data is", length))
```
* matrix()

The matrix of the data is shown below:

```{r}
## The dimension of data
matrix(six_delomys, nrow = 4, ncol = 2)
```
* data.frame()

```{r}
## Create data frame
data.frame(six_delomys, height_delomys, length_delomys)
```


```{r}
## Load the ginkgo data
ginkgo = data.frame(read.csv(here("data", "ginkgo_data_2021.csv")))
head(ginkgo)
```

* nrow()
```{r}
## Get the number of rows
nrow = nrow(ginkgo)
print(paste("The number of rows of ginkgo data is", nrow))
```

* ncol()

```{r}
## Get the number of columns
ncol = ncol(ginkgo)
print(paste("The number of rows of ginkgo data is", ncol))
```

* dim()

```{r}
## Get the dimension of the data
dim = dim(ginkgo)
print(paste("The dimensions of ginkgo data has the column of", dim[1], "and has the rows of", dim[2]))
```

## Subsetting

* Subset a column
```{r}
head(ginkgo)
```

```{r}

## $ Subset a data frame by name: select one of the columns in the ginkgo data

seeds_ginkgo = ginkgo$seeds_present
head(seeds_ginkgo)
```

* select first row of the ginkgo data
```{r}
## Select the first row (col,row)
ginkgo[1,]
```

* select the element in row 2, column 3
```{r}
## Select the second row and third column (col,row)
ginkgo[2,3]
```

* select the 3rd column of the ginkgo data
```{r}
## Select the third column
ginkgo[,3]
```

* subset()
```{r}
## Select the data subset based on the column, according to the species Adelie
subset(penguins, species == 'Adelie')
```


## Numerical Data Exploration
* summary()
```{r}
summary(ginkgo)
```

* mean()
```{r}
mean = mean(ginkgo$notch_depth, na.rm = FALSE)
print(paste("The mean of the notch depth of the ginkgo is", mean))
```

* sd()
```{r}
sd = sd(ginkgo$notch_depth, na.rm = FALSE)
print(paste("The standard deviation of the notch depth of the ginkgo is", sd))
```

## Graphical Data Exploration

* plot()

```{r}
## cex determine the size of point, pch determine the style of point

plot(x= ginkgo$max_depth, 
     y = ginkgo$max_width, 
     main="Depth vs Width of Ginkgo Leaf", 
     xlab="Maximum Depth", 
     ylab="Maximum Width",
     cex=0.8,
     xlim=c(0, max(ginkgo$max_depth)+20),
     ylim=c(0, max(ginkgo$max_width)+20),
     col='blue',
     pch=1)
```

* hist()

```{r}
hist(penguins$flipper_length_mm,
     breaks=10,
     main= "Histogram of Penguins' Flipper Length",
     xlab= "Flipper Length (mm)")
```

* simple boxplot

```{r}
boxplot(ginkgo$petiole_length,
        main="Boxplot of Petiole Length")
```

* conditional boxplot()

```{r}
boxplot(max_depth ~ seeds_present, 
        data = ginkgo,
        xlab =  "Seeds Present",
        ylab = "Maximum Leaf Depth",
        names = c("False", "True")
        )
```

* create 4 histograms

```{r, echo=TRUE, fig.height=10, fig.width=10}
## par assign the values of row and columns of multiple plots

par(mfrow = c(2, 2))
adelie = subset(penguins, species == 'Adelie')
gentoo = subset(penguins, species == 'Gentoo')

hist(adelie$flipper_length_mm,
     breaks=10,
     main= "Histogram of Adelie's Flipper Length",
     xlab= "Flipper Length (mm)")
hist(adelie$bill_length_mm,
     breaks=10,
     main= "Histogram of Adelie's Bill Length",
     xlab= "Bill Length (mm)")
hist(gentoo$flipper_length_mm,
     breaks=10,
     main= "Histogram of Gentoo's Flipper Length",
     xlab= "Flipper Length (mm)")
hist(gentoo$bill_length_mm,
     breaks=10,
     main= "Histogram of Gentoo's Bill Length",
     xlab= "Bill Length (mm)")
```

## Distribution Function

* dnorm()

```{r}
## What is the probability of observing a value exactly 1.5 from a normally-distributed population with mean = 2 and standard deviation = 2?
dnorm(1.5, mean=2, sd=2)
```

* pnorm()

```{r}
## What is the probability of observing a value of less than 1.6 from a normally-distributed population with mean = 2 and standard deviation = 2?

pnorm(1.6, mean = 2, sd = 2)
```

* qnorm()

```{r}
## What is the 20th percentile of the average GRE analytical writing score of 4.5

qnorm(0.2, mean=4.5, sd=1)
```

* dbinom()

```{r}
## What is the probability of observing a count of exactly 2 successes in a binomial distribution with parameters n = 5 and p = 0.75?

dbinom(2,5,0.75)
```

* pbinom()


```{r}
## What is the probability of observing a count of 4 successes or fewer in a binomial distribution with parameters n = 5 and p = 0.75?
pbinom(4,5, 0.75)
```

* qbinom()

```{r}
## What is the 80th percentile of 126 trials and the probability of success is 0.45

qbinom(0.8, 126, 0.45)
```
